The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-18 RET_Hosts_IR.tex

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\hgamma}[0]{H$\gamma$}
\newcommand{\hdelta}[0]{H$\delta$}
\newcommand{\HII}[0]{$[\textnormal{\textsc{Hii}}]$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}

@@

\toprule
{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time \tnote{b} \\
Transient name &  (J2000  & (J2000)  &  (AB)    &         &         &   (hours)         &               \\
\midrule
DES13C3avkj    & 51.97076 & -27.52792 & $24.07 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
DES13X3gms     & 35.80095 &  -4.49384 & $23.02 \pm 0.06$ & 0.6479 &      OzDES &       6.58 \\
DES13C1tgd     & 54.06436 & -27.63867 & $20.30 \pm 0.05$ & 0.1964 &      OzDES &      10.16 \\
DES13C3abtt    & 52.62108 & -28.16151 & $21.50 \pm 0.03$ &    \tnote{d} &          - &             - \\
DES13S2wxf\tnote{e}     & 41.61268 &  -0.02634 & $21.31 \pm 0.03$ & 0.5698 &      OzDES &       5.41 \\
DES13X1hav     & 35.03245 &  -5.11022 & $23.63 \pm 0.07$ & 0.5823 &      OzDES &       4.00 \\
DES13C3smn     & 51.97112 & -28.08362 & $25.30 \pm 0.06$ &    \tnote{c} &      OzDES &             - \\
DES13X3nyg     & 36.99228 &  -3.91327 & $23.38 \pm 0.06$ & 0.7120 &      OzDES &      45.50 \\
DES13X3gmd\tnote{e}     & 36.50409 &  -4.21949 & $22.90 \pm 0.05$ & 0.7808 &      OzDES &      13.91 \\
DES13C3bcok    & 53.02711 & -28.62476 & $18.61 \pm 0.02$ & 0.3457 &  NOAO\_0522 &               \\
DES13X3afjd    & 37.00386 &  -4.58049 & $20.75 \pm 0.05$ &    \tnote{d} &          - &             - \\
DES13C1acmt    & 54.32925 & -26.83371 & $23.18 \pm 0.04$ &    \tnote{c} &      OzDES &             - \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\item[c] Host targetted by OzDES but no redshift measurement possible.
\item[d] Host not targetted by OzDES
\item[e] Found by updated search method (Section \ref{subsec:new_method})
\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method 
\end{tablenotes}
\end{threeparttable}
\label{tab:obs}
\end{table*}

@@

\subsection{Spectroscopy \label{subsec:spec}}
Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner. The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient. The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts. \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}. \replychris{We also obtained redshifts for some transient hosts as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA) survey (PI: A. Baker) \citep{Baker2020} (labelled NOAO in Table \ref{tab:obs}}.
Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.  Where the spectra from which those redshifts were derived are also public they are included in this analysis. These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS. In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel. We stress that the emission lines are detected with a higher SNR than this.

@@

In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}. By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines. An example of this procedure is shown in Fig. \ref{fig:host_spec}. We fit the emission lines with Gaussian profiles. In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution centered on 0, and with a standard deviation equal to the root-mean-square (RMS) of the measured flux noise in a 100~\AA~window around the central wavelength of the line. We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.

@@

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation. Using the Baldwin-Phillips-Terlevich diagram (Fig. \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN.

@@

Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the results from the probability density functions (PDFs) of the various different diagnostics, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and display the results in Table \ref{tab:derived}.

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the scale of PP04 (O3N2) using the conversion from \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we calculate a weighted mean of the values after transforming them to the PP04 O3N2 scale.

@@

\subsection{Star formation rate \label{subsec:res_sfr}}
Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies along with that for the comparison samples and for the field galaxies of SDSS. RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars. The local rapid transients Cow, Koala and SN2018gep are

Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming intensity. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely starforming environments home to LGRBs or SLSNe.

We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions. For both samples, we use identical normal priors for the `loc' (location, i.e. central value, identical to mean \replychris{for zero skewness}) and `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined. The results from the simultaneous fitting are displayed in Appendix \ref{app:b}. The comparison shows RET hosts to be shifted to higher sSFRs CCSNe. In 100\% of the posterior samples the RETs were located at higher average sSFRs than SNe II, while the same was true 76\% of the time for RETs when comparing with SESNe.

RET host galaxies are significantly lower in sSFR than LGRBs. While the distributions are similar in shape, with a mean difference in scale of 0.28, the mean difference in loc is -1.64, with no overlap between the posterior distributions. The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{+1.8}_{-0.98}$ compared to $-0.18^{+0.75}_{-0.76}$ for RET hosts). The strong high-sSFR tail shows SLSNe to \replychris{occur in a different galaxy }population to RETs.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
\caption{The mass-metallicity relation (MZR) for RET host galaxies.
\label{fig:mzr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES. The orange histogram represents the 97/106 DES RETs for which a host was detected. The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
\label{fig:mag_dist}}
\end{figure}

In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars. A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity. Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies. The cumulative distributions of metallicity are displayed in Fig. \ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies. The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe. RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.

>>>>

%define some nice astro shortcuts
\newcommand{\halpha}[0]{H$\alpha$}
\newcommand{\hbeta}[0]{H$\beta$}
\newcommand{\hgamma}[0]{H$\gamma$}
\newcommand{\hdelta}[0]{H$\delta$}
\newcommand{\HII}[0]{$[\textnormal{\textsc{Hii}}]$}
\newcommand{\OII}[0]{$[\textnormal{\textsc{Oii}}]$}
\newcommand{\OI}[0]{$[\textnormal{\textsc{Oi}}]$}
\newcommand{\OIII}[0]{$[\textnormal{\textsc{Oiii}}]$}
\newcommand{\SII}[0]{$[\textnormal{\textsc{Sii}}]$}
\newcommand{\SIII}[0]{$[\textnormal{\textsc{Siii}}]$}
\newcommand{\NII}[0]{$[\textnormal{\textsc{Nii}}]$}
\newcommand{\msun}[0]{M_{\odot}}

@@

{} &       RA &       Dec &    $m_r$\tnote{a}  &     $z$ &     Survey & Exposure time \tnote{b} \\
Transient name &  (J2000  & (J2000)  &  (AB)    &         &         &   (hours)         &               \\
DES13C3avkj    & 51.97076 & -27.52792 & 24.07937 & 0.04534 &    $^c$ &      OzDES &             - \\
DES13X3gms     & 35.80095 &  -4.49384 & 23.02264 & 0.06436 & 0.64792 &      OzDES &       6.58333 \\
DES13C1tgd     & 54.06436 & -27.63867 & 20.30968 & 0.05848 & 0.19647 &      OzDES &      10.16667 \\
DES13C3abtt    & 52.62108 & -28.16151 & 21.50529 & 0.03508 &    $^d$ &          - &             - \\
DES13S2wxf     & 41.61268 &  -0.02634 & 21.31219 & 0.03266 & 0.56985 &      OzDES &       5.41639 \\
DES13X1hav     & 35.03245 &  -5.11022 & 23.63452 & 0.07752 & 0.58236 &      OzDES &       4.00000 \\
DES13C3smn     & 51.97112 & -28.08362 & 25.30041 & 0.06023 &    $^c$ &      OzDES &             - \\
DES13X3nyg     & 36.99228 &  -3.91327 & 23.38744 & 0.06173 & 0.71205 &      OzDES &      45.50000 \\
DES13X3gmd     & 36.50409 &  -4.21949 & 22.90614 & 0.05419 & 0.78082 &      OzDES &      13.91667 \\
DES13C3bcok    & 53.02711 & -28.62476 & 18.61674 & 0.02560 & 0.34577 &  LADUMA &               \\
DES13X3afjd    & 37.00386 &  -4.58049 & 20.75298 & 0.05737 &    $^d$ &          - &             - \\
DES13C1acmt    & 54.32925 & -26.83371 & 23.18742 & 0.04422 &    $^c$ &      OzDES &             - \\
DES13X3kgm     & 36.50380 &  -4.86636 & 26.46803 & 0.18709 &    $^d$ &          - &             - \\
DES13C3uig     & 52.94416 & -27.58544 & 22.17966 & 0.03116 & 0.67346 &       ACES &               \\
DES13C3nxi     & 51.96356 & -28.35720 & 24.99276 & 0.05177 &    $^c$ &      OzDES &             - \\
DES13C3asvu    & 52.83670 & -27.36071 & 22.46669 & 0.02874 &    $^d$ &          - &             - \\
DES13X3pby     & 36.33330 &  -5.31408 & 23.82628 & 0.04671 &    $^c$ &      OzDES &             - \\
DES13X3aakf    & 35.71205 &  -4.69915 & 25.47453 & 0.09478 &    $^c$ &      OzDES &             - \\
DES13X2wvv     & 34.86526 &  -6.71603 & 21.89573 & 0.02567 & 0.47503 &      OzDES &       4.50000 \\
DES13X2oyb     & 35.31056 &  -5.67893 & 22.91589 & 0.06115 &    $^c$ &      OzDES &             - \\
DES13X3alnb    & 37.18496 &  -5.14232 & 25.04147 & 0.06167 &    $^c$ &      OzDES &             - \\
DES15X3atd     & 35.84011 &  -4.29142 & 23.87686 & 0.05432 &    $^c$ &      OzDES &             - \\
DES14S2anq     & 41.27776 &  -0.74529 & 17.57076 & 0.03648 & 0.05211 &      OzDES &       0.75000 \\
DES14E2xsm     &  9.67624 & -43.58736 & 23.39163 & 0.04458 &    $^c$ &      OzDES &             - \\
DES14X1bnh     & 33.74902 &  -4.79254 & 21.95260 & 0.03597 & 0.82982 &      OzDES &       3.50000 \\
DES14E1aqi     &  8.73970 & -43.40182 & 25.61559 & 0.23708 &    $^d$ &          - &             - \\
DES15S1fli     & 43.18790 &  -0.88620 & 20.98517 & 0.02950 & 0.44739 &      OzDES &       2.33333 \\
DES14C3gzj     & 52.57168 & -28.14019 & 26.04181 & 0.10494 &    $^d$ &          - &             - \\
DES14X3pko     & 36.90824 &  -3.69642 & 24.48291 & 0.06326 &    $^d$ &          - &             - \\
DES15S1fll     & 42.78846 &  -0.19747 & 20.95918 & 0.03719 & 0.22647 &      OzDES &       0.66667 \\
DES14C1jnd     & 54.35153 & -27.49300 & 24.33143 & 0.08524 &    $^c$ &      OzDES &             - \\
DES14X3pkl     & 37.21103 &  -4.80741 & 22.40853 & 0.06026 & 0.29537 &      OzDES &       5.16667 \\
DES13X3npb     & 36.64218 &  -4.13381 & 20.79328 & 0.05336 & 0.49542 &      OzDES &       5.16667 \\
DES15X2ead     & 36.48913 &  -6.45118 & 20.08582 & 0.03290 & 0.23175 &      OzDES &       2.00000 \\
DES15C3edw     & 52.55235 & -27.71022 & 22.69331 & 0.03227 &    $^d$ &          - &             - \\
DES14S2plb     & 41.85667 &  -1.61811 & 18.38419 & 0.03463 & 0.11531 &      OzDES &       2.00000 \\
DES14S2pli     & 41.22837 &  -1.09830 & 20.86839 & 0.03093 & 0.35478 &      OzDES &       3.41667 \\
DES15X3kyt     & 36.27500 &  -5.41103 & 24.74520 & 0.07892 &    $^d$ &          - &             - \\
DES14C3tvw     & 53.32230 & -27.90621 & 21.31841 & 0.02516 & 0.70390 &       ACES &               \\
DES14C3tnz     & 52.86248 & -28.51318 & 22.26137 & 0.03386 & 0.70452 &      OzDES &       5.79361 \\
DES15X3mxf     & 36.74009 &  -5.23991 & 22.43347 & 0.04552 & 0.43673 &      OzDES &       9.83333 \\
DES15X3nlv     & 36.04464 &  -5.02735 & 25.26349 & 0.08375 &    $^d$ &          - &             - \\
DES15C3mem     & 52.14216 & -29.05851 & 20.28975 & 0.04590 & 0.61618 &     PRIMUS &               \\
DES15E2lmq     &  9.62005 & -43.98734 & 25.65868 & 0.18116 &    $^d$ &          - &             - \\
DES15C3lpq     & 52.71204 & -28.61319 & 23.28579 & 0.03610 & 0.61365 &      OzDES &       6.16667 \\
DES15C3lzm     & 52.17460 & -28.23186 & 20.47636 & 0.02573 & 0.32690 &      ATLAS &               \\
DES15C3nat     & 52.88528 & -28.72370 & 23.39015 & 0.03154 & 0.83929 &      OzDES &      18.62222 \\
DES15C3mgq     & 52.76901 & -28.20882 & 22.97470 & 0.03194 & 0.23031 &      OzDES &       8.16667 \\
DES15E2nqh     &  9.73174 & -43.08707 & 23.29709 & 0.03941 & 0.51525 &      OzDES &       6.83333 \\
DES15C3opk     & 51.66147 & -28.34737 & 23.05209 & 0.03270 & 0.56984 &      OzDES &      12.16667 \\
DES15C3opp     & 51.73962 & -28.11496 & 23.25950 & 0.04223 & 0.44242 &      OzDES &      16.75000 \\
DES15C3pbi     & 52.23620 & -28.00223 & 25.10028 & 0.05470 &    $^d$ &          - &             - \\
DES16E2pv      &  9.20875 & -43.52782 & 23.00100 & 0.05043 & 0.72608 &      OzDES &       6.00000 \\
DES16S1bbp     & 43.26389 &   0.37149 & 21.42883 & 0.04524 & 0.19018 &      OzDES &       3.33333 \\
DES15X3oma     & 36.74617 &  -5.11040 & 24.94606 & 0.07447 &    $^d$ &          - &             - \\
DES16C3bor     & 52.48232 & -28.04256 & 23.83923 & 0.03711 &    $^c$ &      OzDES &             - \\
DES16C1bde     & 54.30149 & -26.75840 & 24.96313 & 0.09485 &    $^d$ &          - &             - \\
DES16X3wt      & 36.23751 &  -5.54488 & 26.90234 & 0.28423 &    $^d$ &          - &             - \\
DES16X3cxn     & 36.83044 &  -4.95100 & 23.05257 & 0.04442 & 0.58464 &      OzDES &      12.83333 \\
DES16X2bke     & 36.00989 &  -7.27130 & 25.13096 & 0.16403 &    $^d$ &          - &             - \\
DES16C1cbd     & 54.85826 & -27.67254 & 20.93909 & 0.03048 & 0.54108 &      OzDES &       7.20000 \\
DES16C3cdd     & 52.42731 & -27.14317 & 24.27019 & 0.05040 &    $^d$ &          - &             - \\
DES16E1bir     &  7.74444 & -42.97696 & 24.74236 & 0.07595 &    $^c$ &      OzDES &             - \\
DES16C3auv     & 51.90215 & -27.59087 & 24.39158 & 0.05296 &    $^c$ &      OzDES &             - \\
DES16C3axz     & 52.80904 & -28.66678 & 20.41796 & 0.03716 & 0.22673 &  LADUMA &               \\
DES16X3ega     & 37.09820 &  -4.77643 & 19.53601 & 0.04874 & 0.25762 &       GAMA &       1.00000 \\
DES16X3erw     & 36.20545 &  -4.51438 & 22.23157 & 0.02865 & 0.45885 &      OzDES &       2.00000 \\
DES16X1ddm     & 33.82824 &  -4.36428 & 21.46049 & 0.04767 &    $^c$ &      OzDES &             - \\
DES16X3ddi     & 35.43936 &  -4.68602 & 23.93720 & 0.04360 &    $^c$ &      OzDES &             - \\
DES16C3gin     & 52.76276 & -28.29145 & 21.52696 & 0.03653 & 0.34745 &      OzDES &       3.33333 \\
DES16S1dxu     & 42.68141 &  -0.71039 & 21.35662 & 0.03193 & 0.13528 &      OzDES &       1.33333 \\
DES16X1eho     & 35.34537 &  -4.52566 & 22.28516 & 0.07277 & 0.80735 &      OzDES &       6.75000 \\
DES17X3gmp     & 37.40191 &  -4.65060 & 24.44397 & 0.06946 &    $^d$ &          - &             - \\
DES17X2dqk     & 35.46926 &  -7.10815 & 25.96184 & 0.19576 &    $^d$ &          - &             - \\
DES17C3gop     & 53.53574 & -28.40024 & 22.74858 & 0.03107 & 0.69185 &      OzDES &       4.00000 \\
DES17C3gen     & 52.93346 & -29.01119 & 22.79380 & 0.04204 &    $^c$ &      OzDES &             - \\
DES17X3fhq     & 35.93682 &  -3.97690 & 24.70876 & 0.05177 &    $^d$ &          - &             - \\
DES17S2fee     & 41.40953 &  -1.33278 & 18.16644 & 0.04681 & 0.23737 &      OzDES &       2.00000 \\
DES17X1hjj     & 34.24036 &  -4.21180 & 24.07284 & 0.05854 &    $^c$ &      OzDES &             - \\
DES17X1dge     & 34.80886 &  -5.40370 & 24.15755 & 0.10116 &    $^d$ &          - &             - \\
DES17C1fes     & 54.23372 & -27.57015 & 24.42015 & 0.10382 &    $^c$ &      OzDES &             - \\
DES17E1gsx     &  8.11588 & -42.76823 & 22.70982 & 0.04695 &    $^c$ &      OzDES &             - \\
DES17X3dxu     & 36.55911 &  -3.84432 & 22.83789 & 0.03973 & 0.85565 &      OzDES &       7.50000 \\
DES17S1emy     & 43.36298 &   0.41758 & 22.51310 & 0.05326 &    $^d$ &          - &             - \\
DES17X2cvk     & 35.93444 &  -7.32167 & 21.60107 & 0.06456 &    $^d$ &          - &             - \\
DES17X3cdp     & 37.28283 &  -4.30434 & 25.10651 & 0.08381 &    $^c$ &      OzDES &             - \\
DES17X3cds     & 36.27737 &  -3.79891 & 22.45168 & 0.06098 & 0.49444 &      OzDES &       5.50000 \\
DES17C3fwd     & 52.90461 & -27.46979 & 20.46182 & 0.02355 & 0.34561 &    LADUMA &               \\
DES17S1hih     & 42.57627 &  -0.76193 & 24.94967 & 0.12010 &    $^d$ &          - &             - \\
DES17C3fjt     & 51.46785 & -28.14106 & 28.04246 & 0.44157 &    $^d$ &          - &             - \\
DES17X3hxi     & 35.79624 &  -4.51713 & 23.36715 & 0.03375 & 0.62457 &      OzDES &       2.00000 \\
DES13E2lpk     & 10.09911 & -43.53903 & 20.49379 & 0.03567 & 0.47541 &      OzDES &       6.00000 \\
DES15C2eal     & 54.06180 & -29.23000 & 22.99891 & 0.03276 & 0.22347 &      OzDES &      16.90833 \\
DES16C2ggt     & 53.89079 & -29.22496 & 21.09210 & 0.03142 & 0.31057 &      OzDES &       2.66667 \\
DES16C2grk     & 55.06853 & -29.28963 & 20.45434 & 0.03869 &    $^d$ &          - &             - \\
DES17C2hno     & 53.72691 & -29.19742 & 22.69257 & 0.07398 & 0.59953 &      OzDES &       4.66667 \\
\begin{tablenotes}
\item[a] Apparent $r$-band Kron magnitude according to DES-SN deep coadds of \citet{Wiseman2020}, not corrected for Galactic foreground reddening.
\item[b] Exposure time only given for spectra which we have used for line measurements rather than just redshift.
\item[c] Host targetted by OzDES but no redshift measurement possible.
\item[d] Host not targetted by OzDES
\item[e] Found by updated search method (Section \ref{subsec:new_method})
\item[f] Found in Season 5 using \citetalias{Pursiainen2018} method 
\end{tablenotes}
\end{threeparttable}
\label{tab:obs}
\end{table*}

@@

\subsection{Spectroscopy \label{subsec:spec}}
Accurate redshifts for DES-SN were obtained by OzDES, a dedicated DES spectroscopic follow-up campaign based at the $3.9~\textrm{m}$ Anglo-Australian Telescope (AAT) using the AAOmega fibre-fed spectrograph and 2dF fibre positioner. The observation strategy of OzDES was to point at one of the ten DES-SN fields, and place fibres at the positions of transient hosts, continually coadding the spectra of a particular host until a redshift was obtained at which point the fibre could be allocated to a different transient. The spectra have a resolution of 1400-1700 and a wavelength range of $3700~8800$~\AA, and are reduced using the OzDES pipeline which makes use of a modified version of v6.46 of the 2dfdr \citep{Croom2004} along with internal scripts. \replychris{We use internal data release 7, a preliminary version of the public data release is detailed in \citet{Lidman2020}.} Extensive description and discussion of OzDES can be found in \citet{Yuan2015,Childress2017,Lidman2020}. \replychris{We also obtained redshifts for some transient hosts serendipitously as part of the Looking at the Distant Universe with the MeerKAT Array (LADUMA\footnte{\url{http://www.laduma.uct.ac.za}}) survey  \citep{Baker2020}, three of which are present in our sample} .
Objects for which the host already had a publicly available redshift were not observed with OzDES, but merged into the GRC nontheless.  Where the spectra from which those redshifts were derived are also public they are included in this analysis. These comprise the Galaxy and Mass Assembly survey (GAMA \citealt{Driver2009,Baldry2018}) and SDSS. In total we analyse 42 spectra, with a mean continuum signal-to-noise ratio (SNR) of 2.56/pixel. We stress that the emission lines are detected with a higher SNR than this.

@@

In order to subtract the stellar component of the host galaxy spectra, we use the Penalized PiXel-Fitting software (\texttt{pPXF}; \citealt{Cappellari2004,Cappellari2012,Cappellari2017}), using the MILES library of single stellar populations \citep{Vazdekis2010}. By subtracting the best-fitting composite stellar spectrum from the \texttt{pPXF} fit, we are left with a `gas' spectrum, comprising the emission lines. An example of this procedure is shown in Fig. \ref{fig:host_spec}. We fit the emission lines with Gaussian profiles. In order to estimate the uncertainty on the emission line fluxes, we fit $10^4$ realisations of the line, each time adding perturbations to the line by drawing from a Gaussian distribution \replychris{based on the variance spectrum}. We take the mean and standard deviation of the resulting fits as our flux and its uncertainty, respectively.

@@

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation. Using the Baldwin-Phillips-Terlevich diagram (Fig. \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN. \replylluis{We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram. This is also the case for the \SII and \OI versions of the diagram, and we find no evidence AGN amongst the 12 hosts in those diagrams either.}

@@

The samples to which we compare metallicities span different redshift ranges, were observed with different equipment, and in many cases were compiled before certain (particularly the D16) diagnostics were devised. Therefore, in order to compare oxygen abundances between different samples we transform all abundances onto the PP04 O3N2 scale using the conversion from \citet{Kewley2008}. This is not possible for the D16 diagnostic, so we discard it from the rest of our analysis, although for completeness we provide it for DES RET hosts where available. For samples that quoted multiple diagnostics, or for which sufficient line flux measurements were provided from which to calculate multiple diagnostics, we transform them all to the PP04 O3N2 scale. Following the prescription of \citet{Kruehler2015} we simultaneously minimise the oxygen abundance against the probability density functions (PDFs) of the various different diagnostics \replylluis{scaled to PP04 O3N2}, resulting in a final `best' PDF. We take $1\sigma$ uncertainties from the 16th and 84th percentiles of these PDFs, and \replylluis{for DES RETs} display the results in Table \ref{tab:derived}.

@@

\subsection{Star formation rate \label{subsec:res_sfr}}
Fig.~\ref{fig:sfms_sfr} shows the `star formation main sequence' (SFMS) of RET host galaxies, \replychris{as determined from photometric SED fitting} along with that for the comparison samples and for the field galaxies of SDSS. RETs follow CCSNe, LGRBs and SLSNe in systematically avoiding passive galaxies, evidence that RETs require the presence of star-formation and thus are linked to massive stars. The local rapid transients Cow, Koala and SN2018gep \replychris{are lower in mass than the majority of RETs. SN2018gep and Cow lie along the SFMS, while Koala sits in the starburst regime, which is not heavily populated by DES RETs.}

Fig.~\ref{fig:sfms_ssfr} is similar to Fig.~\ref{fig:sfms_sfr}, except that here SFR has been normalised by stellar mass, and thus shows the specific star-formation rate (sSFR), which is more representative measure of the star-forming \replylluis{efficiency}. It is once again clear that RET hosts lie systematically above the majority of SDSS star-forming galaxies. Normalised by mass, it is here perhaps clearer to see that RET hosts lie at higher sSFR than CCSNe hosts, but not in the extremely starforming environments home to LGRBs or SLSNe.

We show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To statistically compare the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions \replylluis{described by the parameters `loc' (location, identical to mean \replychris{for zero skewness}), `scale' (spread, identical to standard deviation for \replychris{zero skewness})\footnote{See \citet{Wiseman2020} for a detailed description of the fitting procedure and the parameters describing the skewed normal distributions}, and `skewness'. To impose priors on loc and scale, we combine the two samples and use normal priors centered on the combined mean and twice the combined standard deviation respectively, while for skewness the prior is a broad normal distribution centered on 0. We note that the loc parameter describes the location of the distribution (its relative position on the x-axis) and is not a mean, median, or mode. A highly-skewed distribution may have a loc that lies above almost the entire sample. A worked example as well as} the results from the simultaneous fitting are displayed in Appendix \ref{app:b}.

The comparison shows RET hosts to be shifted to higher sSFRs CCSNe. In 100\% of the posterior samples the RETs were located at higher average sSFRs than SNe II, while the same was true 76\% of the time for RETs when comparing with SESNe. 
RET host galaxies are significantly lower in sSFR than LGRBs. While the distributions are similar in shape, with a mean difference in scale of 0.28, the mean difference in loc is -1.64, with no overlap between the posterior distributions. The sSFR distribution of SLSNe hosts is heavily positively skewed (with alpha values of $5.54^{+1.8}_{-0.98}$ compared to $-0.18^{+0.75}_{-0.76}$ for RET hosts). The strong high-sSFR tail shows SLSNe to \replychris{occur in a different galaxy }population to RETs.

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
\caption{The mass-metallicity relation (MZR) for RET host galaxies. \replylluis{Upward- and downward-pointing triangles reflect lower and upper limits respectively. The DES RETs with no metallicity measurement have been placed at the top of the figure for completeness.}
\label{fig:mzr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES. The orange histogram represents the 96/106 DES RETs for which a host was detected. The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
\label{fig:mag_dist}}
\end{figure}

In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars. A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity. Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies. The cumulative distributions of metallicity are displayed in Fig. \ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies. The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe. \replylluis{The metallicity distribution of SESNe is, however, quite broad \citep[e.g.][]{Anderson2010}, with different subclasses showing different trends (with SNe Ic host environments exhibiting higher metallicity than Ib, and IIb much lower).} RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.
